### Data

<!--
Step 1: State what data you use and why. Justify your choice of data. Cite the data and say where it is available
-->

#### Parliamentary Bills
My analysis covers 2756 parliamentary bills^[Parliamentary bills include the following nine types of parliamentary proposals that can be introduced in the Swiss parliament (translation provided by the Swiss parliament unless stated otherwise): Parliamentary Initiative (“Parlamentarische Initiative”), Question (“Anfrage”), Urgent Question (own translation: “Dringliche Anfrage”), Interpellation (“Interpellation”), Urgent Interpellation (own translation: “Dringliche Interpellation”), Motions (“Motion”), Postulates (“Postulat”), Question Time – Question (“Fragestunde – Frage”), Petitions (“Petition”)] that include the tag “Environment” (German: “Umwelt”).^[Employees of the Parliamentary Services tag bills with one or several of the following terms that were developed by the Parliamentary Library (Source: Personal email communication with the media spokesperson for the Parliamentary Services): National Policy ("Staatspolitik"), General Law ("Recht Allgemein"), International Politics ("Internationale Politik"), Economy ("Wirtschaft"), Parliament ("Parlament"), Finance ("Finanzwesen"), Social Issues ("Soziale Fragen"), Transportation ("Verkehr"), Environment ("Umwelt"), Urban Planning and Housing ("Raumplanung und Wohnungswesen"), Health ("Gesundheit"), Education ("Bildung"), Media and Communication ("Medien und Kommunikation"), Security Policy ("Sicherheitspolitik"), Agriculture ("Landwirtschaft"), Migration ("Migration"), Science and Research ("Wissenschaft und Forschung"), European Policy ("Europapolitik"), Culture ("Kultur"), Energy ("Energie"), Civil Law ("Zivilrecht"), Employment and Labor ("Beschäftigung und Arbeit"), Human Rights ("Menschenrechte"), Criminal Law ("Strafrecht"), International Law ("Internationales Recht"), Taxation ("Steuer"), Social Protection ("Sozialer Schutz"), Judiciary ("Gerichtswesen”). Own translation from German to English.] These bills were introduced by the SP party (1169 bills) and GPS party (1587 bills) or by their members of parliament in both chambers of the Swiss parliament, namely the National Council (“Nationalrat”) or the Council of States (“Ständerat”). The parliamentary bills are provided by the open data webservices of the Swiss parliament.^[https://www.parlament.ch/de/%C3%BCber-das-parlament/fakten-und-zahlen/open-data-web-services, retrieved 12 May 2024] These webservices are made accessible for further analysis through the R package “swissparl” [@zumbachSwissparlInterfaceWebservices2021].

Central to my analysis is a parliamentary bill’s submitted text. This section is crucial because it is where the author of the bill presents their case and explains the purpose of the bill. The submitted text provides the essential context and rationale for the bill, making it a key element in understanding its intent and focus.

Due to Switzerland’s four official languages, parliamentary items of business can be written either in German, French, Italian or Romansh. The Federal Administration (German: “Bundesverwaltung”) translates most items of business in  to German, French and Italian. Some are only translated into German and French.^[https://www.parlament.ch/de/%C3%BCber-das-parlament/parlamentsw%C3%B6rterbuch/parlamentsw%C3%B6rterbuch-detail?WordId=206, retrieved 14 May 2024] In the context of this research, I have chosen to use parliamentary bills in German, as my German is more proficient than my French, simplifying the examination process.

The bills under examination were introduced between March 2004 and December 2023. I choose this time frame because it coincides with the electoral rise of the GPS and also covers a substantial period before the increased public salience of environmental issues starting in the beginning of the 2010s. This allows for a before-after comparison.

#### Public Salience of Environmental Issues
@luthElectoralImportanceEvolution2022 [171] use the “Swiss Election Study” (Selects)^[https://forscenter.ch/projects/selects/, retrieved 12 May 2024] to measure the salience of environmental issues in the public sphere. In this survey, respondents are asked what their “most important problem” is (Variable “mip1”). I calculate the share of respondents who chose “Environment & Energy” as their most important problem from a list of different issues.^[All issues respondents could pick as their “most important problem”: Agriculture, economics, education and youth & culture, environment & energy, European integration, finances & taxes, gender issues & discrimination, immigration & asylum, international relations&conflicts and foreign policy & army, labour market, law & order, political system and parties & politicians, public health, public service & infrastructure, regions & national cohesion, social security, other problems, no problem, don’t know / no answer / wildcode.] This provides a solid measurement of the public salience of environmental issues. However, the Selects survey is only carried out every four years during Swiss parliamentary elections, thus providing only four data points in my time range of examination (2007, 2011, 2015 and 2019). This stands in contrast to the number of sessions in this time period that I will use to group parliamentary bills by (see “Operationalisation” further below). I thus need a way of measuring public salience of environmental topics on a more frequent basis.

I turn to Google Trends^[https://trends.google.com, retrieved 12 May 2024] as an alternative way to measure public salience. Google Trends is a tool that enables the evaluation of public interest in specific search terms and topics [@nghiemAnalysisCapacityGoogle2016 10]. Data on Google Trends are available from 2004 onwards. I examine the monthly popularity of the search term “climate change” in Switzerland, where data are available between February 2007 and May 2024. I pick the search term “climate change” because it is largely congruent with the same issues that the Selects question described above touches upon. It is thus an adequate way of measuring public salience of environmental topics.

<!-- compare selects with google trends -->
A brief visual comparison of both measures show that both Selects and Google Trends generally follow a similar trend line on environmental issues (see Figure \ref{fig:gt-selects}). This underlines the legitimacy of using Google Trends as a way of measuring public salience of environmental topics.

```{r, child = 'figures/gt_selects.Rmd'}
```


### Operationalisation
<!--
Step 2: Measurement – if you create a new measure using the data, explain how you do so. This could include describing coding procedures, the creation of an index, or other forms of measurement.
-->

#### Dependent Variable: Semantic Similarity between Parliamentary Bills

<!--
ACM: So, in the data section, you can describe what your variables will be and that you will build them using embeddings applied to your raw data.
-->

- in order to measure the semantic similarity between parliamentary bills, i apply word embeddings
- i operationalise the similarity between parliamentary bills as the distance of groups of bills in high-dimensional vector space.
- i do this by using word embeddings to place parliamentary bills in high-dimensional semantic vector space, whereby distances between document correspond to their semantic similarity
- bills that are furhter apart, thus have a higher distance value between each other and are thus less similar.


#### Independent Variable: Measuring Salience of Environmental Issues with Google Trends
Google Trends provides a positive integer value to measure the “search interest” of a term within a specific time frame and geographic region.^[https://trends.google.com, retrieved 13 May 2024] These values are scaled between 0 and 100, reflecting a topic's proportion relative to all searches across all topics.^[https://support.google.com/trends/answer/4365533?hl=en&ref_topic=6248052&sjid=14532437735057784414-EU, retrieved 13 May 2024] When examining the search term "climate change" in Switzerland between February 2007 and May 2024, there is an outlier in April 2022 (see red line in Figure \ref{fig:gt-index}). This is likely due to the United Nation’s Intergovernmental Panel on Climate Change (IPCC) report published in April 2022,^[https://www.ipcc.ch/report/sixth-assessment-report-working-group-3, retrieved 18 May 2024] which was widely discussed in the media.

This outlier, with a value of 100, causes the rest of the data series to display relatively low variation due to the way Google Trends scales values. This low variation becomes more apparent when comparing the Google Trends data up until March 2022 (see blue line in Figure \ref{fig:gt-index}). Low variation is problematic for modelling the data later on, as it makes effects less pronounced. To restore the variation lost in the time series that includes April 2022, I recalculated each value by following these steps: First, I calculate the relative change of each value in the shorter series (blue line) with respect to its first value, obtaining the "multiplier." Second, I align the starting points of both series (blue and red line) by adding a value of 42 to the longer series (red line). Third, I multiply each value in the longer series (red line) by the "multiplier" from the first step. This results in a more pronounced variation in the longer series that mirrors the shorter series (see green line in Figure \ref{fig:gt-index}). Finally, I cap maximum values of the re-indexed series (green line) at 100.

```{r, child = 'figures/gt_index.Rmd'}
```
