## Results

### Correlation Results

```{r, child = 'figures/cor_plot.Rmd'}
```

First, I present the results of the correlation between the change in topic salience and the change in semantic similarity. The correlation coefficient is $0.19$, with borderline statistical significance at conventional levels $(p = 0.11)$. This suggests a positive but weak correlation, indicating that an increase in topic salience is associated with an increase in the semantic distance between the bills, i.e., the bills become less similar. This finding contradicts my theory and does not support my hypothesis.

However, when the time lag is applied to the semantic distance, the results point in the opposite direction. The correlation coefficient between issue salience and *lagged* semantic similarity is $-0.22$, with statistical significance at conventional levels $(p = 0.06)$. This indicates that an increase in public salience of environmental issues is associated with a decrease in semantic distance between parliamentary bills introduced by the SP and the GPS, lagged by one parliamentary session. This decrease in distance suggests that SP and GPS parliamentary bills become more similar over time as public attention to environmental issues increases.

### Linear Regression Results

```{r, child = 'tables/models.Rmd'}
```

Next, I present the results of the linear regression model. The results from the linear regression models are consistent with the results from the correlations. See Table \ref{tab:models} for details. Using the unlagged dependent variable, we observe a positive relationship between the two variables with borderline statistical significance. The model with the lagged dependent variable shows a negative coefficient for the independent variable at a statistically significant level $(p < 0.1)$. This indicates that an increase in the salience of environmental issues is associated with a decrease in Euclidean distance in the following parliamentary session.

The difference between the unlagged and lagged dependent variables in both the correlation analysis and the linear regression models is due to the delayed response of political actions to public opinion. In this research, parliamentary bills are introduced as a reaction to the public's interest in topics. However, this reaction does not occur immediately. The process of introducing parliamentary bills takes time, as they need to be written and political allies must be secured. This shows that it takes time for public opinion to affect legislation.

A caveat regarding the linear regression model results is that the coefficient value cannot be interpreted beyond its sign. The informative value of the coefficient is limited because the distance value between groups of bills can only indicate whether two groups are closer or further apart compared to other groups. Thus we can only interpret the polarity sign of the coefficients and conclude that higher topic salience is associated with groups of bills being closer to each other in semantic space.

Returning to the hypothesis, we cannot reject the possibility that an increase in the public salience of environmental issues is associated with an increase in the content similarity of parliamentary bills. However, for this statement to hold, semantic similarity must be lagged by one parliamentary session. Furthermore, these results can only be generalised to the Swiss case.

Returning to the theory, and based on the results presented above, we can assume that the SP perceives the GPS as an electoral threat and is reacting to this and also to the increased salience of environmental issues amongst the public. The SP responds to this by introducing environmental legislation that is increasingly similar to that of the GPS. The SP sees potential in winning over GPS voters, who are ideologically much closer to its existing base than voters from other parties, by introducing parliamentary bills that are similar in content to those bills introduced by the GPS.

This may be an indication that the SP is becoming more environmentally oriented in an attempt to appeal to green voters. By focusing its legislative efforts more on environmental issues, the SP may be trying to broaden its appeal and capture a segment of the electorate that is increasingly concerned with environmental issues.

The SP’s strategic shift could have wider implications for Swiss politics. If the SP continues to prioritise environmental issues, this could lead to increased competition for green votes, potentially forcing other parties to adapt their agendas to address environmental concerns as well. This dynamic could lead to a more environmentally friendly legislative agenda overall, as parties compete for the support of an electorate that places a higher priority on environmental issues.

In conclusion, the results suggest that the increased public salience of environmental issues leads parties, especially those with overlapping ideological bases such as the SP and GPS, to introduce more similar legislative content. This strategy not only reflects parties' responsiveness to voters' concerns, but also their efforts to remain competitive in an evolving political landscape focused on sustainability and environmental protection.
