## Results

### Correlation Results

```{r, child = 'figures/cor_plot.Rmd'}
```

- i begin by presenting the results of the correlation between the change in topic salience and the change in semantic similarity
- the correlation coefficient equals $0.19$ with borderline statistical significance at conventional levels ($p = 0.11$).
- This suggests a positive but weak correlation, indicating that an increase in topic salience is associated with an increase in semantic distance between bills, i.e., bills being less similar. This would go against my theory and not support my hypothesis.
- However, when applying the time lag to the semantic distance, the results point in the other direction
- The correlation coefficient between topic salience and *lagged* semantic similarity equals $-0.22$ with statistical significance at conventional levels ($p = 0.06$). 
- This indicates that an increase in public salience on environmental topics is associated with a decrease in semantic distance between parliamentary bills, lagged by one parliamentary session. This decrease in distance indicates that parliamentary bills become more similar

### Linear Regression Results

```{r, child = 'tables/models.Rmd'}
```

- in a next step, i present results from the linear regression model.
- see Table \@ref(tab:models) for the results of the linear regression models.
- the results from linear regression models are similar to the results from the correlations.
- when using the un-lagged dependent variable, we observe a positive relationship between the two variables with borderline statistical significance.
- the model with the lagged dependent variable displays a negative coefficient for the independent variable at a statistically significant level ($p < 0.1$).  this indicates that an increase in environmental topic salience is associated with a decrease in semantic distance in the *following* parliamentary session.

- a caveat of the model results is that the coefficient value cannot be interpreted further
- The informative value of the coefficient is limited. because the distance value between groups of bills cannot provide more information than if two groups are close or far from each other – compared to other groups
- in sum, we can only interpret the polarity sign of the coefficients and draw the conclusion that higher topic salience is associated with groups of bills closer to each other in semantic space.

- returning to the hypothesis, we fail to reject the notion that an increase in public salience of environmental issues is associated with an increase in the content similarity between parliamentary bills. however, for this statement to hold, the semantic similarity must be lagged by one parliamentary session. furthermore, the results can only speak for the Swiss case.

so what does this mean?
- returning to the theory and based on the results presented above, we can assume that the sp does perceive the gps as an electoral threat and is reacting to this and the increased salience of environmental topics amongst the public
- the sp reacts to this by introducing environmental bills that have become more similar to parliamentary bills introduced by the greens.
- the sp sees potential in winning over green voters, who are ideologically much closer to their exisiting base than voters from other parties, by introducing parliamentary bills that are similar in content to those introduced by the GPS
- this can be an indication that the sp is becoming more green, in an attempt to be more appealing towards green voters.


<!--
This section describes the results of your analysis. It includes any relevant tables and figures. Wherever possible present figures rather than tables. Describe all figures and tables in words. They do not speak for themselves. But, at the same time, they should also be described well enough in the title, axis labels, and caption that readers can understand the necessary information by looking at the tables/figures alone.

You must discuss both statistical and substantive significance!

As predicted by our theory, we see that [X] has a statistically significant effect on [Y] at the p<0.05 level across all the models that we run.
-->