## Results

### Correlation Results

```{r, child = 'figures/cor_plot.Rmd'}
```

First, I present the results of the correlation between the change in search term popularity and the change in Euclidean distance. The correlation coefficient is $0.19$, with borderline statistical significance at conventional levels $(p = 0.11)$. This suggests a positive but weak correlation, indicating that an increase in search term popularity is associated with an increase in Euclidean distance between the bills, i.e., the bills become less similar. This finding contradicts my theory and does not support my hypothesis.

However, when the time lag is applied to the Euclidean distance, the results point in the opposite direction. The correlation coefficient between the change in search term popularity and the *lagged* change of Euclidean distance is $-0.22$, with statistical significance at conventional levels $(p = 0.06)$. This indicates that an increase of the popularity of the search term “climate change” is associated with a decrease in Euclidean distance between parliamentary bills introduced by the SP and the GPS, lagged by one parliamentary session. This decrease in distance suggests that SP and GPS parliamentary bills become more similar when public attention to environmental issues increases.

### Linear Regression Results

```{r, child = 'tables/models.Rmd'}
```

Next, I present the results of the linear regression model. The results from the linear regression models, displayed in Table \ref{tab:models}, are consistent with the results from the correlations. Using the un-lagged dependent variable (Model 1), we observe a positive relationship between the two variables with borderline statistical significance. Model 2, which applies the lagged dependent variable, shows a negative coefficient for the independent variable at a statistically significant level $(p < 0.1)$. This indicates that an increase in the change of the search term popularity is associated with a decrease in the change of the Euclidean distance in the following parliamentary session.

I assume that the difference between the un-lagged and lagged dependent variables in both the correlation analysis and the linear regression models is due to the delayed response of political actions to public opinion. In this research, parliamentary bills are introduced as a reaction to the public's interest in topics. However, this reaction does not occur immediately. The process of introducing parliamentary bills takes time, as they need to be written and political allies must be secured. This lag shows that it takes time for public opinion to affect legislation.

A caveat regarding the linear regression model results is that the coefficient value cannot be interpreted beyond its sign. The informative value of the coefficient is limited because the distance value between groups of bills can only indicate whether two groups are closer or further apart compared to other groups. Thus we can only interpret the polarity sign of the coefficients and conclude that an increase in the change in search term popularity is associated with a decrease in the Euclidean distance of groups of bills in semantic space.

Returning to the hypothesis, we cannot reject the statement that an increase in the public salience of environmental issues is associated with an increase in the content similarity of parliamentary bills. However, for this statement to hold, semantic similarity must be lagged by one parliamentary session. Furthermore, these results can only be generalised to Switzerland.

Returning to the theory, and based on the results presented above, we can assume that the SP perceives the GPS as an electoral threat and is reacting to this and also to the increased salience of environmental issues amongst the public. The SP responds to this by introducing environmental legislation that is increasingly similar to that of the GPS. The SP sees potential in winning over GPS voters, who are ideologically much closer to its existing base than voters from other parties, by introducing parliamentary bills that are similar in content to those bills introduced by the GPS.

This may be an indication that the SP is becoming more environmentally oriented in an attempt to appeal to GPS voters. By focusing its legislative efforts more on environmental issues, the SP may be trying to broaden its appeal and capture a segment of the electorate that is increasingly concerned with environmental issues.

The SP's strategic shift could have wider implications for Swiss politics. If the SP continues to prioritise environmental issues, and public concern about these issues grows, it could intensify competition for environmentally conscious voters. According to the “party system agenda” theory, this will force other parties to adapt their agendas to include environmental issues. Consequently, this dynamic could lead to a more environmentally friendly legislative agenda overall, as parties compete for the support of an electorate that increasingly prioritises environmental concerns.

In conclusion, the results suggest that the increased public salience of environmental issues leads parties, especially those with overlapping ideological bases such as the SP and GPS, to introduce more similar parliamentary bills. This strategy reflects parties' responsiveness to voters' environmental concerns and their efforts to remain competitive in an evolving political landscape.
