## Results

### Correlation Results

```{r, child = 'figures/cor_plot.Rmd'}
```

First, I present the results of the correlation between the change in topic salience and the change in semantic similarity. The correlation coefficient is $0.19$, with borderline statistical significance at conventional levels $(p = 0.11)$. This suggests a positive but weak correlation, indicating that an increase in topic salience is associated with an increase in the semantic distance between the bills, i.e., the bills become less similar. This finding contradicts my theory and does not support my hypothesis.

However, when the time lag is applied to the semantic distance, the results point in the opposite direction. The correlation coefficient between issue salience and *lagged* semantic similarity is $-0.22$, with statistical significance at conventional levels $(p = 0.06)$. This indicates that an increase in public salience of environmental issues is associated with a decrease in semantic distance between parliamentary bills, lagged by one parliamentary session. This decrease in distance suggests that parliamentary bills become more similar over time as public attention to environmental issues increases.

### Linear Regression Results

```{r, child = 'tables/models.Rmd'}
```

In the next step, I present the results of the linear regression model. See Table \ref{tab:models} for the detailed results of the linear regression models. The results from the linear regression models are consistent with the results from the correlations. Using the unlagged dependent variable, we observe a positive relationship between the two variables with borderline statistical significance. The model with the lagged dependent variable shows a negative coefficient for the independent variable at a statistically significant level $(p < 0.1)$. This indicates that an increase in the salience of environmental issues is associated with a decrease in semantic distance in the following parliamentary session.

A caveat regarding the model results is that the coefficient value cannot be interpreted beyond its sign. The informative value of the coefficient is limited because the distance value between groups of bills can only indicate whether two groups are closer or further apart compared to other groups. In summary, we can only interpret the polarity sign of the coefficients and conclude that higher topic salience is associated with groups of bills being closer to each other in semantic space.

Returning to the hypothesis, we cannot reject the possibility that an increase in the public salience of environmental issues is associated with an increase in the content similarity of parliamentary bills. However, for this statement to hold, semantic similarity must be lagged by one parliamentary session. Furthermore, these results can only be generalised to the Swiss case.

Returning to the theory, and based on the results presented above, we can assume that the SP perceives the GPS as an electoral threat and is reacting to this and to the increased salience of environmental issues in the public eye. The SP has responded by introducing environmental legislation that is increasingly similar to that of the GPS. The SP sees potential in winning over GPS voters, who are ideologically much closer to its existing base than voters from other parties, by introducing parliamentary bills that are similar in content to those introduced by the GPS.

This may be an indication that the SP is becoming more environmentally oriented in an attempt to appeal to green voters. By focusing its legislative efforts more on environmental issues, the SP may be trying to broaden its appeal and capture a segment of the electorate that is increasingly concerned with environmental issues.

Moreover, this strategic shift could have wider implications for the political landscape in Switzerland. If the SP continues to prioritise environmental issues, this could lead to increased competition for green votes, potentially forcing other parties to adapt their platforms to address environmental concerns more robustly. This dynamic could lead to a more environmentally conscious legislative agenda overall, as parties compete for the support of an electorate that places a higher priority on sustainability and climate change.

In conclusion, the results suggest that the increased public salience of environmental issues leads parties, especially those with overlapping ideological bases such as the SP and GPS, to introduce more similar legislative content. This strategy not only reflects parties' responsiveness to voters' concerns, but also their efforts to remain competitive in an evolving political landscape focused on sustainability and environmental protection.

<!--
This section describes the results of your analysis. It includes any relevant tables and figures. Wherever possible present figures rather than tables. Describe all figures and tables in words. They do not speak for themselves. But, at the same time, they should also be described well enough in the title, axis labels, and caption that readers can understand the necessary information by looking at the tables/figures alone.

You must discuss both statistical and substantive significance!

As predicted by our theory, we see that [X] has a statistically significant effect on [Y] at the p<0.05 level across all the models that we run.
-->