## Results

### Descriptive Analysis

```{r, child = 'tables/counts.Rmd'}
```

Table \ref{tab:counts} gives an overview of the number of bills introduced in the Swiss parliament between March 2004 and December 2023. During this period, approximately 12.7% of all bills introduced contained the tag "environment". The SP introduced more than twice as many bills in all categories as the GPS, but around 400 fewer bills on environmental issues. Approximately 10.5% of SP bills dealt with environmental issues, while almost 30% of GPS bills dealt with environmental issues. These differences are logical as the SP has more seats in parliament than the GPS (see Figure \ref{fig:ch-parties}) and environmental issues are more central to the GPS agenda.

```{r, child = 'figures/all_bills.Rmd'}
```

Figure \ref{fig:all-bills} shows how the number of all parliamentary bills has increased over the last 20 years. The number of bills introduced by the SP and the GPS has remained mostly constant, except for an increase after the 2019 election, when the GPS achieved its best election result in history. Comparing the number of bills with an environmental label with all bills, the number of environmental bills remained more or less constant until the early 2010s. After this period, there was a slow increase until the late 2010s, followed by a sharp increase.

```{r, child = 'figures/env_party_bills.Rmd'}
```

If we break down the number of environmental bills by party (Figure \ref{fig:env-party-bills}), we can see that all parties introduced roughly the same number of these bills until the late 2010s. Around 2019, all parties started to introduce more environmental bills, with the SP and GPS leading the way. After this brief spike, all parties except the GPS reduced their number of environmental bills. Again, this makes intuitive sense, as the GPS owns green issues and had just come off a very successful election in 2019.

<!--
nice to have:
- bills by party strength, incl. graph
- show number of bills by party strength; divide number of bills from a party by seats in parliament
-->

In summary, while the total number of parliamentary bills has increased over the past 20 years, the number of environmental bills remained largely unchanged until the late 2010s. It was during this period that there was a notable increase in the number of environmental bills introduced in the Swiss parliament. The GPS appears to be a driving force behind many of these bills, with the SP also introducing a significant number of environmental bills compared to other major parties in the Swiss parliament.

In the next step, I examine the lengths of the bills introduced by counting the number of words in each bill. This is relevant because measuring content similarity by calculating the embedding of a bill requires calculating the embedding of each word. Consequently, the more words in a single bill, the more information is available, leading to a more precise placement of the bill in semantic space. If the number of words varied significantly between bills, this could have a negative impact on the accuracy of the analysis.

```{r, child = 'figures/wc_bills.Rmd'}
```

Figure \ref{fig:wc-bills} shows that the number of words in all bills (median: 72 words) and the number of words in environmental bills (median: 74 words) are almost the same. Over time, the number of words in bills remains stable, with the standard deviation of the median for each year being 7.72 for all bills and 12.49 for environmental bills. A similar stability is observed for environmental bills introduced by the SP and the GPS, with the standard deviation of the median over time being 13.77 for SP bills and 14.95 for GPS bills. 

In summary, this brief examination of bill length shows that the number of words per bill remains fairly consistent over time. This consistency is beneficial for the application of a text-as-data approach, as it ensures that a comparable amount of data is available per bill throughout the period under study.

### Inferential Analysis

#### Correlation Results

```{r, child = 'figures/cor_plot.Rmd'}
```

First, I present the results of the correlation between the change in search term popularity and the change in Euclidean distance. The correlation coefficient is $0.19$, with borderline statistical significance at conventional levels $(p = 0.11)$. This suggests a positive but weak correlation, indicating that an increase in search term popularity is associated with an increase in Euclidean distance between the bills, i.e., the bills become less similar. This finding contradicts my theory and does not support my hypothesis.

However, when the time lag is applied to the Euclidean distance, the results point in the opposite direction. The correlation coefficient between the change in search term popularity and the *lagged* change of Euclidean distance is $-0.22$, with statistical significance at conventional levels $(p = 0.06)$. This indicates that an increase of the popularity of the search term “climate change” is associated with a decrease in Euclidean distance between parliamentary bills introduced by the SP and the GPS, lagged by one parliamentary session. This decrease in distance suggests that SP and GPS parliamentary bills become more similar when public attention to environmental issues increases.

#### Linear Regression Results

```{r, child = 'tables/models.Rmd'}
```

Next, I present the results of the linear regression model. The results from the linear regression models, displayed in Table \ref{tab:models}, are consistent with the results from the correlations. Using the un-lagged dependent variable (Model 1), we observe a positive relationship between the two variables with borderline statistical significance. Model 2, which applies the lagged dependent variable, shows a negative coefficient for the independent variable at a statistically significant level $(p < 0.1)$. This indicates that an increase in the change of the search term popularity is associated with a decrease in the change of the Euclidean distance in the following parliamentary session.

I assume that the difference between the un-lagged and lagged dependent variables in both the correlation analysis and the linear regression models is due to the delayed response of political actions to public opinion. In this research, parliamentary bills are introduced as a reaction to the public's interest in topics. However, this reaction does not occur immediately. The process of introducing parliamentary bills takes time, as they need to be written and political allies must be secured. This lag shows that it takes time for public opinion to affect legislation.

A caveat regarding the linear regression model results is that the coefficient value cannot be interpreted beyond its sign. The informative value of the coefficient is limited because the distance value between groups of bills can only indicate whether two groups are closer or further apart compared to other groups. Thus we can only interpret the polarity sign of the coefficients and conclude that an increase in the change in search term popularity is associated with a decrease in the Euclidean distance of groups of bills in semantic space.

Returning to the hypothesis, we cannot reject the statement that an increase in the public salience of environmental issues is associated with an increase in the content similarity of parliamentary bills. However, for this statement to hold, semantic similarity must be lagged by one parliamentary session. Furthermore, these results can only be generalised to Switzerland.

Returning to the theory, and based on the results presented above, we can assume that the SP perceives the GPS as an electoral threat and is reacting to this and also to the increased salience of environmental issues amongst the public. The SP responds to this by introducing environmental legislation that is increasingly similar to that of the GPS. The SP sees potential in winning over GPS voters, who are ideologically much closer to its existing base than voters from other parties, by introducing parliamentary bills that are similar in content to those bills introduced by the GPS.

This may be an indication that the SP is becoming more environmentally oriented in an attempt to appeal to GPS voters. By focusing its legislative efforts more on environmental issues, the SP may be trying to broaden its appeal and capture a segment of the electorate that is increasingly concerned with environmental issues.

The SP's strategic shift could have wider implications for Swiss politics. If the SP continues to prioritise environmental issues, and public concern about these issues grows, it could intensify competition for environmentally conscious voters. According to the “party system agenda” theory, this will force other parties to adapt their agendas to include environmental issues. Consequently, this dynamic could lead to a more environmentally friendly legislative agenda overall, as parties compete for the support of an electorate that increasingly prioritises environmental concerns.

In conclusion, the results suggest that the increased public salience of environmental issues leads parties, especially those with overlapping ideological bases such as the SP and GPS, to introduce more similar parliamentary bills. This strategy reflects parties' responsiveness to voters' environmental concerns and their efforts to remain competitive in an evolving political landscape.
